Figures

### 2020-03-04 figures/07_model-selection_nolulc.Rmd
fix cutoff labels

```{r fe_nolulc}
cowplot::plot_grid(
cowplot::plot_grid(
  equalize_panels(
    gg_tp_fe + theme(axis.title.x = element_blank())
  ), 
  equalize_panels(
    gg_tn_fe + 
      theme(axis.text.y = element_blank(), 
            axis.title.x = element_blank())), 
  rel_widths = c(1, 0.95)),

>>>>

```{r fe_nolulc, fig.width=7.5}
cowplot::plot_grid(
cowplot::plot_grid(
  equalize_panels(
    gg_tp_fe + theme(axis.title.x = element_blank())
  ), 
  equalize_panels(
    gg_tn_fe + 
      theme(axis.text.y = element_blank(), 
            axis.title.x = element_blank())), 
  rel_widths = c(1, 0.95)),
